Automated Formal Synthesis\\ of Safe Digital Controllers for Continuous Plants

### 2018-05-15 automatica/paper.tex
rephrased the objective EG2
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\item[EG2] \textbf{(Sanity check)} Confirm the
stability and safety of the synthesized controllers \note{[this is unclear, rephrase:]outside of our model.}

>>>>

\item[EG2] \textbf{(Sanity check)} \textcolor{blue}{Confirm the stability and safety of the synthesized controllers outside 
of our model representation using MATLAB}.
